---
title: "Lab 3 Task 1 Binomial Logistic Regression"
author: "Peyton Moore"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```



```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species))

# levels(adelie_chinstrap$species) to check factor levels 


```

Let's just dataviz of those two species 


```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm))+
  geom_point(aes(color = sex))+
  facet_wrap(~species)
```


Binary logistic regression 

- body mass 
- flipper length
- penguin sex 

```{r}

adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm +sex, 
                            data = adelie_chinstrap, 
                            family = "binomial")
```


take a look at the outcomes: 

```{r}
summary(adelie_chinstrap_blr)
```

because levels are 
 1. Adelie 
 2. Chinstrap 
 
model is telling us the probability of the penguin beind a chinstrap 

positive coefficients mean increasing changes of being a chinstrap 
flipper length is only significantly non zero predictor variable 


Always align coefficients with what you're seeing in the data 

```{r}
ggplot(data= adelie_chinstrap, aes(x = species, y = flipper_length_mm))+
  geom_jitter(aes(color = sex))
```
looks like chiinstrap seem to have larger flippers 
yay! thats what our model told us too


What are the actual probabilities of being chinstrap for all of the existing observations in our data frame?

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
#fitted column shows probability that the penguin is chinstrap 



```

Plotting fitted probabilities: 

```{r}
ggplot(data = blr_fitted, aes(x = flipper_length_mm, y = .fitted))+
  geom_point(aes(color = sex, pch = species))+
  geom_smooth(aes(color = sex), se = FALSE)+
  labs(x = "Flipper Length (mm)", 
       y = "Probability of Outcome Chinstrap")
```
Plot model based on different variables 

```{r}
effect_plot(adelie_chinstrap_blr, 
            pred = flipper_length_mm, 
            y.label = "Probability of Chinstrap", 
            interval = TRUE)

effect_plot(adelie_chinstrap_blr, 
            pred = body_mass_g,  
            y.label = "Probability of Chinstrap", 
            interval = TRUE)
```
What's the probability that a female penguin weighing 3410g with a flipper length of 192mm is a Chinstrap? 

```{r}
ex_1 <- predict(adelie_chinstrap_blr, 
                data.frame(sex = "female", 
                           body_mass_g = 3410, 
                           flipper_length_mm = 192), 
                type = "response")
ex_1

```


